Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-06 paper.tex
more improvements to the introduction

This work proposes learning DSLs.
We consider the setting where we have a collection of related programming tasks,
each specified by a set of input/output examples.
Our algorithm, called \system,
does two things:
it finds programs that solve each of the tasks,
and at the same time creates its own DSL by discovering and reusing
new domain-specific subroutines.
The idea is that induced DSL
should distill the commonalities across the programs that solve the tasks,
and so can be used to solve other related program learning problems.

@@

  \end{tikzpicture}
  \caption{(a) DSL $\mathcal{D}$ generates programs $p$ by sampling DSL primitives with probabilities $\theta$ (Algorithm~\ref{programGenerativeModel}). Observe tasks $x$ (program inputs/outputs). (b)  neural network $q(\cdot )$, the \emph{recognition model}, regresses from $x$ to a distribution over programs
    ($\theta^{(x)} = q(x)$). Black arrows correspond to the top-down generative model. Red arrows correspond to the bottom-up recognition model.}\label{graphicalModel}
\end{figure}

@@

Inference in the generative model in Figure~\ref{graphicalModel}(a) is
difficult because the programs are unobserved, and so we must solve a
difficult search problem to find any programs at all. To make
inference tractable our model learns a bottom-up \emph{recognition
  model} alongside the top-down generative model
(Figure~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from observations to a distribution over
programs.  The neural network $q$ implements an amortized
inference/compiled inference
scheme~\cite{le2016inference,ritchie2016deep} for the generative
model.

@@

The neural architecture of $q$ depends upon the domain;
for domains with sequential structure like strings and lists,
we use an RNN,
and for domains with a fixed-dimensionality inputs/outputs we use a multilayer perceptron.

>>>>

This work proposes learning DSLs.
We consider the setting where we have a collection of related programming tasks,
each specified by a set of input/output examples.
We do not assume that the tasks are annotated with
ground-truth programs.
Our algorithm, called \system,
does two things:
it finds programs that solve each of the tasks,
and at the same time creates its own DSL by discovering and reusing
domain-specific subroutines.
The learned DSL
should distill the commonalities across the programs that solve the tasks,
and so can be used to solve other related program learning problems.

@@

  \end{tikzpicture}
  \caption{(a) DSL $\mathcal{D}$ generates programs $p$ by sampling DSL primitives with probabilities $\theta$ (Algorithm~\ref{programGenerativeModel}). Observe tasks $x$ (program inputs/outputs). (b)  Neural network $q(\cdot )$, the \emph{recognition model}, regresses from $x$ to the parameters of a distribution over programs
    ($\theta^{(x)} = q(x)$). Black arrows correspond to the top-down generative model. Red arrows correspond to the bottom-up recognition model.}\label{graphicalModel}
\end{figure}

@@

Inference in the generative model in Figure~\ref{graphicalModel}(a) is
complicated by the fact that the programs are unobserved latent variables,
and so we must solve a difficult search problem to find any programs at all. To make
inference tractable our model learns a bottom-up \emph{recognition
  model} alongside the top-down generative model
(Figure~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs.  The neural network $q$ implements an amortized
inference/compiled inference
scheme~\cite{le2016inference,ritchie2016deep} for the generative
model by speeding up the search for programs.

@@

The neural architecture of $q$ depends upon the domain.
For domains with sequential structure like strings and lists,
we use an RNN to encode each input/output example,
and for domains with a fixed-dimensionality inputs/outputs we use a multilayer perceptron.
We MaxPool across all of the input/output examples. See supplement for more details on the neural architecture.
